WSClean: an implementation of a fast, generic wide-field imager

### 2014-02-27 articles/2014/Article-WSClean/wsclean.tex
Adding full-sky image

TODO: add big full-sky image (PKS J2358-6054 is visible)

>>>>

\begin{figure*}
\begin{center}
\includegraphics[width=13.5cm]{img/fullsky-together}
\caption{A beam-corrected MWA image of a 112~s zenith observation that covers almost the full sky. The lower image shows a zoom-in on the southern side lobe. PKS J2358-6054 ($\sim100$ Jy) is visible in the centre of the southern side lobe and resolved. The noise level in the side lobe is about 200 mJy.}
\label{fig:full-sky-example}
\end{center}
\end{figure*}
